Quantifying and partitioning uncertainties in retrievals of plant traits from imaging spectroscopy data

### 2020-12-03 manuscript/manuscript.tex
More work on manuscript methods

For a given combination of surface elevation and atmospheric conditions (aerosol optical depth and water vapor content), we simulated

@@

@@

We quantified the contributions of each uncertainty source to both estimates of surface reflectance and the final trait estimates.

>>>>

In our experiment, we calculated these values over a factorial combination of atmospheric conditions, sun-sensor geometries, and additional mission characteristics (Table~\ref{tab:combinations}).
For atmospheric conditions and surface elevation, we considered ten combinations identified as representative of global conditions (REF).
These combinations included
aerosol optical depth at 550 nm (AOD) ranging from 0.09 to 0.802,
water vapor content ranging from 0.543 to 4.323 g cm$^{-2}$,
surface elevation ranging from 77 to 3571 m above sea level,
and two types of atmospheric profiles (REF): tropical and midlatitude summer (Table~\ref{tab:atmospheres}).
For sun-sensor geometries, we considered a factorial combination of observation dates and times (which, combined with observation location, determine the position of the sun), sensor zenith angle, and sensor relative (to the sun's position) azimuth angle.

\begin{table}
\caption{\label{tab:atmospheres} Globally-representative atmospheres used in this analysis.}
\centering
\begin{tabular}{lllll}
\hline
  Global relative abundance (\%)  & Surface elevation (m) & Aerosol optical depth & Water vapor (g cm$^{-2}$) & Profile type  \\
  \hline
  34.0 & 109 & 0.090 & 1.190 & Midlatitude summer \\
  13.8 & 105 & 0.123 & 2.716 & Midlatitude summer \\
  12.6 & 77 & 0.132 & 2.889 & Tropical \\
  9.1 & 1174 & 0.100 & 1.116 & Midlatitude summer \\
  8.7 & 263 & 0.350 & 1.748 & Midlatitude summer \\
  8.7 & 88 & 0.168 & 4.323 & Tropical \\
  5.5 & 233 & 0.445 & 2.936 & Tropical \\
  4.5 & 911 & 0.135 & 1.853 & Tropical \\
  2.4 & 227 & 0.802 & 2.611 & Tropical \\
  0.7 & 3571 & 0.138 & 0.543 & Midlatitude summer \\
\hline
\end{tabular}
\end{table}

\begin{table}
\caption{\label{tab:combinations} Factorial combination of inputs}
\centering
\begin{tabular}{p{0.2\linewidth}lp{0.4\linewidth}p{0.3\linewidth}}
  \hline
  Variable & Size & Values & Comments \\
  \hline
  Atmosphere & 10 & \emph{See Table~\ref{tab:atmospheres}} & \\ 
  \hline
  Constellation inter-calibration scale & 3 & 0, 16, 32 & & \\
  Constellation atmospheric noise (\%) & 4 & 0, 1, 5, 10 & & \\
  Constellation angular noise (\%) & 4 & 0, 1, 5, 10 & & \\
  \hline
  Local time (24H) & 10 & 9:30, 10:00, 10:15, 10:30, 10:45, 11, 12, 13:30, 15:00 & Spaced over the day, with denser sampling around typical ``A-train'' satellite overpass around 10:30AM \\
  Date & 7 & March 20, May 20, June 20, July 20, August 20, September 22, December 21 & Northern hemisphere equinoxes and solstices, as well as denser sampling in summer (when traits are typically mapped) \\
  Sensor zenith (degrees) & 6 & 0, 12.5, 25, 37.5, 50, 75  & \\
  Sensor relative azimuth (degrees) & 5 & 0, 30, 60, 90, 180 & \\
  \hline
  Total grid size & \multicolumn{3}{l}{21,000} & & \\
  \hline
\end{tabular}
\end{table}

@@

Algorithms from \citeA{singh2015imaging}.
Algorithms from \citeA{chadwick2020integrating}.

@@

We quantified the contributions of each uncertainty source to both estimates of surface reflectance and the final trait estimates.
Partitioning uncertainty.

Quantifying retrieval accuracy.
Quantifying bias.
